A Systematic Approach to Analyzing Syndication of Viral News Stories

### 2019-12-07 paper/paper.tex
Sending the file up

\subsection{Dataset Creation}
\subsubsection{Identification of Viral News Article}
Like in phase I, we did not use articles published by unbiased media sources and steered clear of stories related to Donald Trump. An article with more than \emph{ten thousand reactions}\footnote{reaction is the sum of likes, comments and shares} on facebook was quantified as a viral news article. The articles selected in the end were a heterogenous mixture of local and international events. These new articles were used to manually build\emph{url.csv} dataset. This dataset consists of a single feature, namely the url pointing to the article.

\subsubsection{Scraping similar news articles}

>>>>

\subsection{Dataset Creation}
\subsubsection{Identification of Viral News Article}
Like in phase I, we did not use articles published by unbiased media sources and steered clear of stories related to Donald Trump. An article with more than \emph{ten thousand reactions}\footnote{reaction is the sum of likes, comments and shares} on facebook was quantified as a viral news article. The articles selected in the end were a heterogenous mixture of local and international events. These new articles were used to manually build\emph{url.csv} dataset. This dataset consists of a single feature, url pointing to the article.

\subsubsection{Scraping similar news articles}
Once a url.csv is generated, remanining articles are fetched manually of the internet. Currently, we use google news api and newsapi to query for the relevant articles.
The urls in \emph{url.csv} were used to generate a temporary dataset which consists of the url of the story along with the title of the story. The title is
